\trtitle\\[0.3cm]{\normalsize\trtype}

### 2024-01-27 Paper/main.tex
Add unknown and category comparison

A known problem with \ac{GAN}s is mode collapse. This phenomenon describes models which focus on the most common feature in the dataset to generate new images. Instead of generating diverse samples that cover the entire data distribution, the generator might focus on generating samples with certain features. This lack of diversity in the generated data can be seen in the class "only head".\\
This category includes the Pokémon "Unknown", which mimics the Latin alphabet and thus has 28 variations. Though different, all variations follow the same design rules, black lines and one eye. Accounting for all different image types 53\% of the images in this category were just depicting some variation of this Pokémon. This can be seen in the results generated for this class. Mainly, most of th generated images follow the "Unknown" design. Examples can be seen in Figure \ref{fig:}. This mode collapse can be avoided by filtering the images within the class.

>>>>

A known problem with \ac{GAN}s is mode collapse. This phenomenon describes models which focus on the most common feature in the dataset to generate new images. Instead of generating diverse samples that cover the entire data distribution, the generator might focus on generating samples with certain features. This lack of diversity in the generated data can be seen in the class "only head".\\
This category includes the Pokémon "Unknown", which mimics the Latin alphabet and thus has 28 variations. Though different, all variations follow the same design rules, black lines and one eye. Accounting for all different image types 53\% of the images in this category were just depicting some variation of this Pokémon. This can be seen in the results generated for this class. Mainly, most of th generated images follow the "Unknown" design. Examples can be seen in Figure \ref{fig:unknownvariety}. This mode collapse can be avoided by filtering the images within the class.\\
This can be avoided by using sub sampling i.e. train more on the Pokémons in this category that are represented less.

Moreover, there is a noticeable difference in the coherence of images among classes. Images generated for a specific class exhibit greater similarities, whereas other classes display a higher variance in the generated images. This is illustrated in Figure \ref{fig:}. The samples generated for the class "quadrupled" differ more strongly in comparison to images generated for the class "winged".

\begin{figure}[H]
	\centering
	\includegraphics[width=0.5\linewidth]{src/Images/head_generated}
	\caption[Generated images for head]{Different generated images for the head category. It can be seen that the model replicates the design of the Pokémon "Unknown".}
	\label{fig:unknownvariety}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.9\linewidth]{src/Images/category_comparison}
	\caption[Class Comparison]{Comparison between classes}
	\label{fig:categorycomparison}
\end{figure}
